---
title: "Estimating Feed Efficiency in Assaf ewes"
author: "Pablo Fonseca, Gonzalo Hervás, and Juan Jose Arranz"
date: '2023-02-08'
output:
  html_document: default
  '': default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r setup_tables, echo=FALSE, results='asis'}
library(knitr)
library(tidyr)
library(kableExtra)
```

## Importing database with phenotypic values

The database used here is composed of 39 Assaf ewes in the first lactation which had the estrus synchronized and the lambing performed in a short window in order to avoid variations caused by the lactation stage. These animals were housed in individual pens and were milked twice a day in a 1x10 stall milking parlor (DeLaval). In the first stage, these animals were fed ad libitum a total mixed ratio (TMR) formulated from alfalfa hay (particle size > 4 cm) and concentrates (50:50 forage:concentrate ratio). These ewes had their dry matter intake (DMI) and milk yield measured daily for a period of three weeks after a period of three weeks of adaptation to the TMR. For each animal, the feed intake was estimated daily by weighting the dry matter refused. Additionally, morning and evening milk production was weighted for each animal in order to calculate the daily milk yield. Protein, fat, and lactose content were estimated for each animal as described by Barrio et al. (2022). The changes in the body weight (BW) were calculated by each ewe through the recording of two consecutive days at the beginning and at the end of the FE evaluation. 


```{r }
#Replace the pathway by the folder in your computer

FE.db<-read.table("~/post_doc_Leon/projetos/RFI_sheep_R_calculations/databases_FE/FE_AllMetrics_database_sheep_07_02_23.txt", h=T, sep="\t")

head(FE.db)
```

The following columns are observed in the database:

*Animal_ID:* Animal identification

*Treatment:* Categorical variable indicating if the animals was subjected or not to a protein restriction (~40% reduction) challenge 

*meanBW:* Average body weight (kg)

*BWC1:* Body weight change during the experimental period

*days_period:* Days in the experiment

*Fat:* Fat yeild (g/kg)

*Protein:* Protein yield (g/kg)

*Milk:* Milk yield (kg/d)

*intake:* Actual dry matter intake

*energyTMR:* Energy content of the total mixed ratio (TMR)

*DIM:* Days in milk


## Importing required libraries and functions

```{r }
library(ggplot2)
library(PerformanceAnalytics)
library(plotly)
library(patchwork)
```

```{r}
#Defining custom theme for plots in the document
custom_theme<-function(){
  theme(panel.grid.major = element_line(colour = "#d3d3d3"),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 14, face = "bold"),
        axis.title = element_text(face="bold", size=20),
        axis.text.x = element_text(colour="black", size = 20, angle = 0),
        axis.text.y = element_text(colour="black", size = 20),
        axis.line = element_line(size=0.5, colour = "black"),
        legend.title = element_text(size = 25),
        legend.text = element_text(size=20),
        strip.text.x = element_text(size = 15))
        }
```

## Estimating additional metrics for FEI, FCR and RFI calculations

In order to calculate the FE metrics, some additional values must be estimated.

*Body weight change during the period (BWC2)*

```{r }
#Defined as the body weight change during the whole period divided by the days 
#in the period

FE.db$BWC2<-FE.db$BWC1/FE.db$days_period
```

*Metabolic body weight*

```{r }
#Defined as the body weight raised to 0.75

FE.db$MBW<-FE.db$meanBW^0.75
```

*Energy requirements for BW change, UFL/d*

```{r }
#Defined based on INRA equations

FE.db$ER_BWC<-(0.28*(FE.db$BWC2*1000))/100
```

*Energy requirements for maintenance, UFL/d*

```{r }
#Defined based on INRA equations

FE.db$ER_main<-(0.0345*FE.db$MBW)
```


*Mean milk yield, L/d (MY)*

```{r }
FE.db$MY<-FE.db$Milk/1.036
```

*Fat yield, L/d (MY)*

```{r }
FE.db$FY<-FE.db$Fat/1.036
```

*Protein yield, L/d (MY)*

```{r }
FE.db$PY<-FE.db$Protein/1.036
```

*Metabolic body weight change per day*

```{r }
#Defined as the absolute BWC1 raised to 0.75

FE.db$MBWC1<-abs(FE.db$BWC1)^0.75
```


*Metabolic body weight change for the experimental period*

```{r }
#Defined as the absolute BWC2 raised to 0.75

FE.db$MBWC2<-abs(FE.db$BWC2)^0.75
```


*Energy corrected milk (ECM, kg/d) - INRA 2018*

```{r }
#Defined based on INRA equations

FE.db$ECM<-FE.db$MY*(0.0071*FE.db$FY+0.0043*FE.db$PY+0.2224)
```

*Energy requirements for milk yield, UFL/d*

```{r }
#Defined based on INRA equations

FE.db$ER_MY<-0.686*FE.db$ECM
```

*Total energy requirements, UFL/d*

```{r }
#Defined as the sum of the Energy requirements for MY, maintenance, and BWC

FE.db$TER<-rowSums(FE.db[,c("ER_MY","ER_main","ER_BWC")])
```

*Predicted DM intake*

```{r }
#Defined as the ratio between total energy requirements and the energy on TMR

FE.db$Pred_DMI<-FE.db$TER/FE.db$energyTMR
```


**Checking new database**

```{r }
head(FE.db)
```


## Estimating FEI and FCR

After the estimation of the additional metrics above mentioned, the estimation of FCR and FEI it is a straightforward approach.

### *Feed efficiency index (FEI)*

```{r }
#FEI is defined as Actual dry matter intake subtracted by the predicted dry matter intake

FE.db$FEI<-FE.db$intake-FE.db$Pred_DMI
```

```{r FEI_distribution,}
#Checking distribution of FEI values

ggplot(FE.db, aes(x=FEI)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme() 

#Checking correlation between FEI and actual intake values

cor_FEI_DMI<-round(cor(FE.db$intake, FE.db$FEI),2)

text_FEI<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(FE.db$intake,2), "\n" ,
                "FEI: ", round(FE.db$FEI,2),sep="")

FEI_plot<-ggplot(FE.db, aes(y=intake,x=FEI, text=text_FEI)) + 
  geom_point() + 
  custom_theme() + scale_y_continuous(name="DMI") +
  ggtitle(paste("Actual DMI vs FEI (r2= ", cor_FEI_DMI,")",sep=""))

ggplotly(FEI_plot, tooltip = "text")

```


### *Feed Conversion Ratio (FCR)*

```{r }
#FCR is defined as Feed intake (kg DM/d) / ECM (kg/d), where ECM is estimated based on the ECM equation from INRA 2018 (for sheep) 

FE.db$FCR<-FE.db$intake/FE.db$ECM
```

```{r FCR_distribution,}
#Checking distribution of FCR values

ggplot(FE.db, aes(x=FCR)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme() 

#Checking correlation between FCR and actual intake values

cor_FCR_DMI<-round(cor(FE.db$intake, FE.db$FCR),2)

text_FCR<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(FE.db$intake,2), "\n" ,
                "FCR: ", round(FE.db$FCR,2),sep="")

FCR_plot<-ggplot(FE.db, aes(y=intake,x=FCR, text=text_FCR)) + 
  geom_point() + 
  custom_theme() + scale_y_continuous(name="DMI") +
  ggtitle(paste("Actual DMI vs FCR (r2= ", cor_FCR_DMI,")",sep=""))

ggplotly(FCR_plot, tooltip = "text")

```


## Estimating Residual feed intake (RFI)

The RFI is defined as the subtraction of the actual feed intake by the predicted feed intake. The prediction of feed intake can be performed using different models. Here, for models to predict the feed intake and subsequently the RFI will be shown.

*RFI estimation based on the model proposed by Pryce et al. 2015*

````{r}
#A linear model including ECM, MBW, BWC1 and DIM is used to predict the feed intake

model.pryce<-lm(intake ~ ECM + MBW + BWC1 + DIM,data=FE.db)

#Checking model output

summary(model.pryce)

#Extracting residuals (RFI)
FE.db$RFI_pryce<-residuals(model.pryce)

head(FE.db$RFI_pryce)

#Checking distribution of RFI_pryce values

ggplot(FE.db, aes(x=RFI_pryce)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme() 

#Checking the correlation between predicted and actual values

r2_pryce<-round(summary(model.pryce)$adj.r.squared,3)

RFI_pryce_table<-data.frame(DMI=FE.db$intake, predicted_DMI=predict(model.pryce))

text_pryce<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(RFI_pryce_table$DMI,2), "\n" ,
                "RFI_pryce: ", round(RFI_pryce_table$predicted_DMI,2),sep="")

plot_pryce<-ggplot(RFI_pryce_table, aes(y=DMI,x=predicted_DMI, text=text_pryce)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle(paste("Actual DMI vs predicted DMI by pryce (r2= ", r2_pryce,")",sep=""))

ggplotly(plot_pryce, tooltip = "text")


````


*RFI estimation based on ECM, MBW and MBWC2*

````{r}
#A linear model including ECM, MBW and MBWC2 is used to predict the feed intake

model.RFI2<-lm(intake ~ ECM + MBW + MBWC2,data=FE.db)

#Checking model output

summary(model.RFI2)

#Extracting residuals (RFI)
FE.db$RFI2<-residuals(model.RFI2)

head(FE.db$RFI2)

#Checking distribution of RFI_pryce values

ggplot(FE.db, aes(x=RFI2)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme()

#Checking the correlation between predicted and actual values

r2_RFI2<-round(summary(model.RFI2)$adj.r.squared,3)

RFI_RFI2_table<-data.frame(DMI=FE.db$intake, predicted_DMI=predict(model.RFI2))

text_RFI2<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(RFI_RFI2_table$DMI,2), "\n" ,
                "RFI2: ", round(RFI_RFI2_table$predicted_DMI,2),sep="")

plot_RFI2<-ggplot(RFI_RFI2_table, aes(y=DMI,x=predicted_DMI, text=text_RFI2)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle(paste("Actual DMI vs predicted DMI by RFI2 (r2= ", r2_RFI2,")",sep=""))

ggplotly(plot_RFI2, tooltip = "text")

````



*RFI estimation based on ECM, MBW and an interaction between MeanBW and BWC2*

````{r}
#A linear model including ECM, MBW and an interaction term between meanBW and BWC2 is used to predict the feed intake

model.RFI3<-lm(intake ~ ECM + MBW + meanBW*BWC2,data=FE.db)

#Checking model output

summary(model.RFI3)

#Extracting residuals (RFI)
FE.db$RFI3<-residuals(model.RFI3)

head(FE.db$RFI3)

#Checking distribution of RFI_pryce values

ggplot(FE.db, aes(x=RFI3)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme()

#Checking the correlation between predicted and actual values

r2_RFI3<-round(summary(model.RFI3)$adj.r.squared,3)

RFI_RFI3_table<-data.frame(DMI=FE.db$intake, predicted_DMI=predict(model.RFI3))

text_RFI3<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(RFI_RFI3_table$DMI,2), "\n" ,
                "RFI3: ", round(RFI_RFI3_table$predicted_DMI,2),sep="")

plot_RFI3<-ggplot(RFI_RFI3_table, aes(y=DMI,x=predicted_DMI, text=text_RFI3)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle(paste("Actual DMI vs predicted DMI by pryce (r2= ", r2_RFI3,")",sep=""))

ggplotly(plot_RFI3, tooltip = "text")

````

## Estimating correlation between FE metrics

The Pearson correlation across the FE variables estimated here will be calculated and plotted using the R package PerformanceAnalytics. It is possible to note that, in general, a strong correlation is observed between the variables. 

````{r}
chart.Correlation(FE.db[,c("FEI","FCR", "RFI_pryce", "RFI2", "RFI3")], histogram=TRUE, pch=19)
````

## Creating a final database with FE metrics

Let's create a final databse containing only the Animal Id and the FE metrics estimated in the last steps.

````{r}
#Filtering the database created in this tutorial based on the column names
FE.metrics<-FE.db[,c("Animal_ID","Treatment","FEI","FCR", "RFI_pryce", "RFI2", "RFI3")]

head(FE.metrics)

````

This database could be save in your computer using the following code: 

````{r, eval = FALSE}
#Filtering the database created in this tutorial based on the column names
write.table(FE.metrics, file="Feed_EfficiencyMetrics_smarter.txt", col.names=T, row.names=F, sep="\t", quote=F)
````

This will create the tab-delimited file "Feed_EfficiencyMetrics_smarter.txt" in your work directory.


## Checking the effect of protein restriction over feed efficiency

The animals which composed the database analyzed here were subject to a nutritional protein restriction (NPR). Initially, 40 lamb ewes from a single flock in the northwest region of Castilla y León (Spain) that were transported to the facilities of the IGM in León were fed a standard diet for replacement ewe lambs providing 16% crude protein until three months of age and were subsequently divided into two groups. The two experimental groups were composed of 20 NPR and 20 C animals. To evaluate the impact of feed restriction challenge due to a trade market problem and a shortage of concentrate inputs, the C ewes received the standard diet mentioned above for 64 d; during the same period, the NPR ewes received the same diet without soybean meal (44% reduction in protein intake). The 64-d NPR period in the prepuberal stage was coincident with the allometric growth of the mammary gland. Now, we will evaluate if the feed efficiency metrics estimated here are significantly different between control and challenge groups. 


### **FEI**

````{r}
# Here we will compare the means of FEI between control and challenge groups using a t-test. But first, we need to define if there is variance equality between groups.

var.test(FEI ~ Treatment, data=FE.metrics)

#The result results of the variance equality test (p-value = 0.3758) suggest that the variances are equal between groups. Therefore, we are assuming this in the t-test. 

t.test(FEI ~ Treatment, data=FE.metrics, var.equal = TRUE)

````


### **FCR**

````{r}
# Here we will compare the means of FCR between control and challenge groups using a t-test. But first, we need to define if there is variance equality between groups.

var.test(FCR ~ Treatment, data=FE.metrics)

#The result results of the variance equality test (p-value = 0.9814) suggest that the variances are equal between groups. Therefore, we are assuming this in the t-test. 

t.test(FCR ~ Treatment, data=FE.metrics, var.equal = TRUE)

````



### **RFI pryce**

````{r}
# Here we will compare the means of RFI_pryce between control and challenge groups using a t-test. But first, we need to define if there is variance equality between groups.

var.test(RFI_pryce ~ Treatment, data=FE.metrics)

#The result results of the variance equality test (p-value = 0.7907) suggest that the variances are equal between groups. Therefore, we are assuming this in the t-test. 

t.test(RFI_pryce ~ Treatment, data=FE.metrics, var.equal = TRUE)

````


### **RFI2**

````{r}
# Here we will compare the means of RFI2 between control and challenge groups using a t-test. But first, we need to define if there is variance equality between groups.

var.test(RFI2 ~ Treatment, data=FE.metrics)

#The result results of the variance equality test (p-value = 0.1377) suggest that the variances are equal between groups. Therefore, we are assuming this in the t-test. 

t.test(RFI2 ~ Treatment, data=FE.metrics, var.equal = TRUE)

````


### **RFI3**

````{r}
# Here we will compare the means of RFI3 between control and challenge groups using a t-test. But first, we need to define if there is variance equality between groups.

var.test(RFI3 ~ Treatment, data=FE.metrics)

#The result results of the variance equality test (p-value = 0.765) suggest that the variances are equal between groups. Therefore, we are assuming this in the t-test. 

t.test(RFI3 ~ Treatment, data=FE.metrics, var.equal = TRUE)

````


We can also check the distribution of each value within control and challenge groups using boxplots.

````{r, fig.dim = c(10, 6)}
#FEI
FEI_NPR_plot<-ggplot(FE.metrics, aes(y=FEI,x=Treatment, fill=Treatment)) + 
  geom_boxplot() + scale_x_discrete(name = "NPR Groups") +
  theme_bw() + scale_fill_manual(values=c("chartreuse", "brown3")) + 
  ggtitle("FEI")

#FCR
FCR_NPR_plot<-ggplot(FE.metrics, aes(y=FCR,x=Treatment, fill=Treatment)) + 
  geom_boxplot() + scale_x_discrete(name = "NPR Groups") +
  theme_bw() + scale_fill_manual(values=c("chartreuse", "brown3")) + 
  ggtitle("FCR")

#RFI_pryce
RFI_pryce_NPR_plot<-ggplot(FE.metrics, aes(y=RFI_pryce,x=Treatment, fill=Treatment)) + 
  geom_boxplot() + scale_x_discrete(name = "NPR Groups") +
  theme_bw() + scale_fill_manual(values=c("chartreuse", "brown3")) + 
  ggtitle("RFI_pryce")


#RFI2
RFI2_NPR_plot<-ggplot(FE.metrics, aes(y=RFI2,x=Treatment, fill=Treatment)) + 
  geom_boxplot() + scale_x_discrete(name = "NPR Groups") +
  theme_bw() + scale_fill_manual(values=c("chartreuse", "brown3")) + 
  ggtitle("RFI2")

#RFI3
RFI3_NPR_plot<-ggplot(FE.metrics, aes(y=RFI3,x=Treatment, fill=Treatment)) + 
  geom_boxplot() + scale_x_discrete(name = "NPR Groups") +
  theme_bw() + scale_fill_manual(values=c("chartreuse", "brown3")) + 
  ggtitle("RFI3")


(FEI_NPR_plot | FCR_NPR_plot) / (RFI_pryce_NPR_plot | RFI2_NPR_plot | RFI3_NPR_plot)


````

## Additional comment

If we check the summary of the models used here to estimate RFI, we will notice that the intercept is not significant for any model. Consequently, what would happen if we exclude the intercept from our models? But, even more important... Should we remove the intercept from our model in this case?

*RFI estimation based on the model proposed by Pryce et al. 2015*

````{r}
#A linear model including ECM, MBW, BWC1 and DIM is used to predict the feed intake

model.pryce_NoInt<-lm(intake ~ 0 + ECM + MBW + BWC1 + DIM,data=FE.db)

#Checking model output

summary(model.pryce_NoInt)

#Extracting residuals (RFI)
FE.db$RFI_pryce_NoInt<-residuals(model.pryce_NoInt)

head(FE.db$RFI_pryce_NoInt)

#Checking distribution of RFI_pryce_NoInt values

ggplot(FE.db, aes(x=RFI_pryce_NoInt)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme() 

#Checking the correlation between predicted and actual values

r2_pryce_NoInt<-round(summary(model.pryce)$adj.r.squared,3)

RFI_pryce_NoInt_table<-data.frame(DMI=FE.db$intake, predicted_DMI=predict(model.pryce))

text_pryce_NoInt<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(RFI_pryce_NoInt_table$DMI,2), "\n" ,
                "RFI_pryce_NoInt: ", 
                round(RFI_pryce_NoInt_table$predicted_DMI,2),sep="")

plot_pryce_NoInt<-ggplot(RFI_pryce_NoInt_table, aes(y=DMI,x=predicted_DMI, text=text_pryce_NoInt)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle(paste("Actual DMI vs predicted DMI by pryce (r2= ", r2_pryce_NoInt,")",sep=""))

ggplotly(plot_pryce_NoInt, tooltip = "text")


````


*RFI estimation based on ECM, MBW and MBWC2*

````{r}
#A linear model including ECM, MBW and MBWC2 is used to predict the feed intake

model.RFI2_NoInt<-lm(intake ~ 0 + ECM + MBW + MBWC2,data=FE.db)

#Checking model output

summary(model.RFI2_NoInt)

#Extracting residuals (RFI)
FE.db$RFI2_NoInt<-residuals(model.RFI2_NoInt)

head(FE.db$RFI2_NoInt)

#Checking distribution of RFI_pryce values

ggplot(FE.db, aes(x=RFI2_NoInt)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme()

#Checking the correlation between predicted and actual values

r2_RFI2_NoInt<-round(summary(model.RFI2_NoInt)$adj.r.squared,3)

RFI_RFI2_NoInt_table<-data.frame(DMI=FE.db$intake, predicted_DMI=predict(model.RFI2_NoInt))

text_RFI2_NoInt<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(RFI_RFI2_NoInt_table$DMI,2), "\n" ,
                "RFI2_NoInt: ", 
                round(RFI_RFI2_NoInt_table$predicted_DMI,2),sep="")

plot_RFI2_NoInt<-ggplot(RFI_RFI2_NoInt_table, aes(y=DMI,x=predicted_DMI, text=text_RFI2_NoInt)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle(paste("Actual DMI vs predicted DMI by RFI2 (r2= ", r2_RFI2_NoInt,")",sep=""))

ggplotly(plot_RFI2_NoInt, tooltip = "text")

````



*RFI estimation based on ECM, MBW and an interaction between MeanBW and BWC2*

````{r}
#A linear model including ECM, MBW and an interaction term between meanBW and BWC2 is used to predict the feed intake

model.RFI3_NoInt<-lm(intake ~ 0 + ECM + MBW + meanBW*BWC2,data=FE.db)

#Checking model output

summary(model.RFI3_NoInt)

#Extracting residuals (RFI)
FE.db$RFI3_NoInt<-residuals(model.RFI3_NoInt)

head(FE.db$RFI3_NoInt)

#Checking distribution of RFI_pryce values

ggplot(FE.db, aes(x=RFI3_NoInt)) + 
  geom_histogram(color="black", fill="white") + 
  custom_theme()

#Checking the correlation between predicted and actual values

r2_RFI3_NoInt<-round(summary(model.RFI3_NoInt)$adj.r.squared,3)

RFI_RFI3_NoInt_table<-data.frame(DMI=FE.db$intake, predicted_DMI=predict(model.RFI3_NoInt))

text_RFI3_NoInt<-paste("Animal ID: ", FE.db$Animal_ID, "\n","DMI: ", 
                round(RFI_RFI3_NoInt_table$DMI,2), "\n" ,
                "RFI3_NoInt: ", 
                round(RFI_RFI3_NoInt_table$predicted_DMI,2),sep="")

plot_RFI3_NoInt<-ggplot(RFI_RFI3_NoInt_table, aes(y=DMI,x=predicted_DMI, text=text_RFI3_NoInt)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle(paste("Actual DMI vs predicted DMI by RFI3 (r2= ", r2_RFI3_NoInt,")",sep=""))

ggplotly(plot_RFI3_NoInt, tooltip = "text")


````


It is posisble to note that much higher adjusted R-squares were obtained for all the models. However, should we trust on those values?


**Problems when you remove the intercept**

Let's use the models with higher R-adjusted with intercept and its version without intercept as example. First, we should check the distribution of the residuals obtained in both models.


````{r}
# Checking the mean and standard deviation of the residuals obtained in each model

table.res<-data.frame(res_pryce=residuals(model.pryce), res_pryce_NoInt=residuals(model.pryce_NoInt))

head(table.res)
````

```{r setup_RFI_table, echo=FALSE}
res.out<-data.frame(Mean=round(c(mean(table.res$res_pryce), mean(table.res$res_pryce_NoInt)),4), SD=round(c(sd(table.res$res_pryce), sd(table.res$res_pryce_NoInt)),4))

rownames(res.out)<-c("RFI Pryce", "RFI Pryce without intercept")

kable(res.out, caption="Mean and standard deviation of the residuals obtained in the models based on Pryce et al. (2015) with and without intercept.") %>%
  kable_styling(full_width = F)

```

```{r, fig.dim = c(10, 6)}

res.pryce<-ggplot(model.pryce, aes(y=.resid,x=.fitted)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle("RFI Pryce et al. (2015)") + 
  custom_theme() + scale_y_continuous(name="Residuals") +
  scale_x_continuous(name="Fitted values") 

res.pryce.NoInt<-ggplot(model.pryce_NoInt, aes(y=.resid,x=.fitted)) + 
  geom_point() + 
  custom_theme() + 
  ggtitle("RFI Pryce et al. (2015) without intercept") + 
  custom_theme() + scale_y_continuous(name="Residuals") +
  scale_x_continuous(name="Fitted values") 
  
res.pryce | res.pryce.NoInt

```

**Conclusion about intercept removal**

As we can note, the SD obtained for the residuals in both models are quite similar. However, the mean of the residuals in the model without intercept is not equal zero, which is a requirement for the kind of model used here. Additionally, when we remove the intercept, we force the program to set the this value to be equal zero. Consequently, assuming that our the intercepts of our regression lines pass through the zero, which is not the case of most of the models fitted with real data (in the case of a continuous variable). In summary, to run a model without intercept, in the current case, result in an inflation of the sums of squares (SS) for the model (SSmodel) and residuals (SSresidual), leading to the increase in the R-square values.



